### 2015-02-20 fundamentals/impl.tex
simplification

Regression tests ensure unexpected backwards-incompatible changes do not
occur over the course of \Cyclus development. Such a change is called a
\emph{regression} because the new version is almost always wrong.
Regression tests are implemented similarly to integration tests.
Nose is used to execute full \Cyclus simulations whose results
are then compared. In this category, however, the comparison is done against
the output of the same input file when run with a previous version of \Cyclus,
typically the last released version.
In some sense, regression tests are `dumb' in that they do
not care about the contents of a simulation being correct, only whether or not
it changed. They pick up glaring time-sensitive mistakes that may
not appear elsewhere, though they do not purport to make claims about the
quality of the physics modeled. Regression tests are primarily implemented
in \Cycamore because its archetypes are sophisticated enough
to make interesting input files. Only a handful ($<10$) of time steps are needed
for regression testing.

>>>>

Regression tests ensure unexpected backwards-incompatible changes do not
occur over the course of \Cyclus development. Such a change is called a
\emph{regression} because the new version is almost always wrong.
Regression tests are implemented similarly to integration tests.
Nose is used to execute full \Cyclus simulations whose results
are then compared. In this category, however, the comparison is done against
the output of the same input file when run with a previous version of \Cyclus,
typically the last released version.
In some sense, regression tests are `dumb' in that they do
not care about the contents of a simulation being correct, only whether or not
it changed. They pick up glaring time-sensitive mistakes that may
not appear elsewhere, though they do not purport to make claims about the
quality of the physics modeled. Regression tests are primarily implemented
in \Cycamore because its archetypes are sophisticated enough
to make interesting simulations.
